Deployable Probabilistic Programming

### 2019-06-18 paper/paper.tex
minor typos fixed in the paper

Based on the experience of developing and deploying solutions
using different probabilistic environments, we came up with
guidelines to implementation of a probabilistic programming
facility for server-side applications. We believe that these
guidelines, when followed, help easier integration of
probabilistic programming inference into large-scale 
software systems.

@@

For inference, Infergo relies on automatic differentiation. The
source code of the model is translated by the command-line tool
into an equivalent model with reverse-mode automatic
differentiation of the log-likelihood with respect to the
parameters applied. The differentiation operates on the built-in
floating-point type and incurs only a small computational
overhead. However, even this overhead is avoided when the model
code is executed outside of inference algorithms: both the
original and the differentiated model are simultaneously
available to the rest of the program code, so the methods can be
called on the differentiated model for inference, and on the
original model for the most efficient execution with the
inferred parameters.

>>>>

Based on the experience of developing and deploying solutions
using different probabilistic programming environments, we came
up with guidelines to implementation of a probabilistic
programming facility for server-side applications. We believe
that these guidelines, when followed, help easier integration of
probabilistic programming inference into large-scale software
systems.

@@

For inference, Infergo relies on automatic differentiation. The
source code of the model is translated by the command-line tool
into an equivalent model with reverse-mode automatic
differentiation of the log-likelihood with respect to the
parameters applied. The differentiation operates on the built-in
floating-point type and incurs only a small computational
overhead. However, even this overhead is avoided when the model
code is executed outside inference algorithms: both the original
and the differentiated model are simultaneously available to the
rest of the program code, so the methods can be called on the
differentiated model for inference, and on the original model
for the most efficient execution with the inferred parameters.
